Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex
number fix

Four of the presented candidates have FPP $>$90\%;
these are considered to be likely false positives.
On the other hand, 20 candidates
have FPP $<$ 1\%.  
Two of these are found to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.  
Four more of these 21 might plausibly be caused by 
contamination by detected stellar companions within the photometric apertures 
(see \S\ref{sec:background}), so we keep these as candidates.

@@

We emphasize that the majority of these validations rely
solely on the transit photometry and SDSS data, with no need for follow-up imaging.  This
demonstrates the utility of the \texttt{vespa} tool, which will be
crucial to interpreting future candidates detected by \KT, TESS, and PLATO
and prioritizing follow-up observing efforts.
We show the transit signals in Fig. \ref{fig:transits}.

>>>>

Four of the presented candidates have FPP $>$90\%;
these are considered to be likely false positives.
On the other hand, 21 candidates
have FPP $<$ 1\%.  
Two of these are found to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.  
Four more of these 21 might plausibly be caused by 
contamination by detected stellar companions within the photometric apertures 
(see \S\ref{sec:background}), so we keep these as candidates.

@@

We emphasize that the majority of these validations rely
solely on the transit photometry and SDSS data, with follow-up imaging only obtained for
seven of the 31 targets.  This
demonstrates the utility of the \texttt{vespa} tool, which will be
crucial to interpreting future candidates detected by \KT, TESS, and PLATO
and prioritizing follow-up observing efforts.
We show the transit signals in Fig. \ref{fig:transits}.
